---
title: "Getting FPL data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting FPL data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

```{r setup}
library(fantasy)
```
One of the ways to use {fantasy} is for extracting data from the FPL API for further analysis. This might be in order to analyse good players to sign, track your progress over the season, or even build a machine learning model to make team decisions for you. There are a few different types of data that can be extracted.

The sections below show the most useful functions for extracting data - note that none of these require authentication so can be used without account details.

## Fixtures
```{r get-fixtures}
# Get a list of all fixtures for the season, with scores, gameweek and difficulty.
get_fixture_list()

# Get a (long) table of stats for each game, including:
# goals, penalties assists, cards, saves etc.
get_fixture_stats()

# Get information on all the gameweeks
get_gameweek_info()

# Get the current gameweek
get_current_gameweek()
```

## Teams (Premier League teams)
```{r get-teams}
# Get premier league teams with their record so far this season and various strength ratings
get_teams()

# Get the likely starting XIs for the next gameweek, from fantasyfootballscout.co.uk
get_predicted_lineups()
```

## Players
```{r get-players}
# Get all players and their info
get_players()

# Get season summary for a specific player
get_player_summary(player_id = 273)
```
